Single Bivalent Level Analysis

### 2020-01-29 doc/Bivalent_Analysis.Rmd
new pattern for sex diffs in IFDs

#plot the differences
wsb.ploty_IFD <- ggplot(WSB.Bivalents.DF[WSB.Bivalents.DF$hand.foci.count == 2,],  aes(y=IFD1_ABS, x = sex, color= as.factor(mouse)))+geom_jitter()+ggtitle("")
wsb.ploty_IFD

@@

@@

@@

@@

@@

@@

@@

>>>>

#plot the differences
wsb.ploty_IFD_raw <- ggplot(WSB.Bivalents.DF[WSB.Bivalents.DF$hand.foci.count == 2,],  aes(y=IFD1_ABS, x = sex))+
                          geom_jitter()+ggtitle("Raw IFD, WSB")+geom_boxplot(aes(x=sex))
wsb.ploty_IFD_raw

wsb.ploty_IFD_PER <- ggplot(WSB.Bivalents.DF[WSB.Bivalents.DF$hand.foci.count == 2,],  aes(y=IFD1_PER, x = sex))+
                          geom_jitter()+ggtitle("Percent IFD, WSB")+geom_boxplot(aes(x=sex))
wsb.ploty_IFD_PER

@@

#plot the differences
LEW.ploty <- ggplot(LEW.Bivalents.DF,  aes(y=chromosomeLength, x = sex, color= as.factor(hand.foci.count)))+geom_jitter()+ggtitle("")
LEW.ploty
#remove the NAs

wsb.ploty_IFD_raw <- ggplot(WSB.Bivalents.DF[WSB.Bivalents.DF$hand.foci.count == 2,],  aes(y=IFD1_ABS, x = sex))+
                          geom_jitter()+ggtitle("Raw IFD, WSB")+geom_boxplot(aes(x=sex))
wsb.ploty_IFD_raw

wsb.ploty_IFD_PER <- ggplot(WSB.Bivalents.DF[WSB.Bivalents.DF$hand.foci.count == 2,],  aes(y=IFD1_PER, x = sex))+
                          geom_jitter()+ggtitle("Percent IFD, WSB")+geom_boxplot(aes(x=sex))
wsb.ploty_IFD_PER

@@

#plot the metric
#remove the NAs

G.ploty_IFD_raw <- ggplot(G.Bivalents.DF[G.Bivalents.DF$hand.foci.count == 2,],  aes(y=IFD1_ABS, x = sex))+
                          geom_jitter()+ggtitle("Raw IFD, G")+geom_boxplot(aes(x=sex))
G.ploty_IFD_raw

#
G.ploty_IFD_PER <- ggplot(G.Bivalents.DF[G.Bivalents.DF$hand.foci.count == 2,],  aes(y=IFD1_PER, x = sex))+
                          geom_jitter()+ggtitle("Percent IFD, G")+geom_boxplot(aes(x=sex))
G.ploty_IFD_PER

@@

#plot the differences
#remove the NAs

PWD.ploty_IFD_raw <- ggplot(PWD.Bivalents.DF[PWD.Bivalents.DF$hand.foci.count == 2,],  aes(y=IFD1_ABS, x = sex))+
                          geom_jitter()+ggtitle("Raw IFD, PWD")+geom_boxplot(aes(x=sex))
PWD.ploty_IFD_raw

PWD.ploty_IFD_PER <- ggplot(WSB.Bivalents.DF[WSB.Bivalents.DF$hand.foci.count == 2,],  aes(y=IFD1_PER, x = sex))+
                          geom_jitter()+ggtitle("Percent IFD, PWD")+geom_boxplot(aes(x=sex))
PWD.ploty_IFD_PER

@@

#plot the differences

#remove the NAs
KAZ.ploty_IFD_raw <- ggplot(KAZ.Bivalents.DF[KAZ.Bivalents.DF$hand.foci.count == 2,],  aes(y=IFD1_ABS, x = sex))+
                          geom_jitter()+ggtitle("Raw IFD, KAZ")+geom_boxplot(aes(x=sex))
KAZ.ploty_IFD_raw

KAZ.ploty_IFD_PER <- ggplot(KAZ.Bivalents.DF[KAZ.Bivalents.DF$hand.foci.count == 2,],  aes(y=IFD1_PER, x = sex))+
                          geom_jitter()+ggtitle("Percent IFD, KAZ")+geom_boxplot(aes(x=sex))
KAZ.ploty_IFD_PER

@@

#plot the differences

#remove the NAs
SKIVE.ploty_IFD_raw <- ggplot(SKIVE.Bivalents.DF[SKIVE.Bivalents.DF$hand.foci.count == 2,],  aes(y=IFD1_ABS, x = sex))+
                          geom_jitter()+ggtitle("Raw IFD, SKIVE")+geom_boxplot(aes(x=sex))
SKIVE.ploty_IFD_raw

SKIVE.ploty_IFD_PER <- ggplot(SKIVE.Bivalents.DF[SKIVE.Bivalents.DF$hand.foci.count == 2,],  aes(y=IFD1_PER, x = sex))+
                          geom_jitter()+ggtitle("Percent IFD, SKIVE")+geom_boxplot(aes(x=sex))
SKIVE.ploty_IFD_PER

@@

MSM.ploty_IFD_raw <- ggplot(MSM.Bivalents.DF[MSM.Bivalents.DF$hand.foci.count == 2,],  aes(y=IFD1_ABS, x = sex))+
                          geom_jitter()+ggtitle("Raw IFD, MSM")+geom_boxplot(aes(x=sex))
MSM.ploty_IFD_raw

MSM.ploty_IFD_PER <- ggplot(MSM.Bivalents.DF[MSM.Bivalents.DF$hand.foci.count == 2,],  aes(y=IFD1_PER, x = sex))+
                          geom_jitter()+ggtitle("Percent IFD, MSM")+geom_boxplot(aes(x=sex))
MSM.ploty_IFD_PER

#another plot
MSM.IFD_another.plot <- ggplot(MSM.Bivalents.DF[MSM.Bivalents.DF$hand.foci.count == 2,],  aes(y=IFD1_ABS, x = chromosomeLength, color = sex))+                          geom_jitter()+ggtitle("MSM")

MSM.IFDnorm_another.plot <- ggplot(MSM.Bivalents.DF[MSM.Bivalents.DF$hand.foci.count == 2,],  aes(y=IFD1_PER, x = chromosomeLength, color = sex))+                          geom_jitter()+ggtitle("MSM")+ylim(c(0,1.1))

#this plot helps illustrate sex-specific differences for normalized IFDs -- both sexes have a large class / proportion of bivalents with similar IFD_PER values -- but the mean in females is lower due to them having MORE low IFD_PER values

@@

MOLF.ploty
#remove the NAs
molf.ploty_IFD_raw <- ggplot(MOLF.Bivalents.DF[MOLF.Bivalents.DF$hand.foci.count == 2,],  aes(y=IFD1_ABS, x = sex))+
                          geom_jitter()+ggtitle("Raw IFD, MOLF")+geom_boxplot(aes(x=sex))
molf.ploty_IFD_raw

molf.ploty_IFD_PER <- ggplot(MOLF.Bivalents.DF[MOLF.Bivalents.DF$hand.foci.count == 2,],  aes(y=IFD1_PER, x = sex))+
                          geom_jitter()+ggtitle("Percent IFD, MOLF")+geom_boxplot(aes(x=sex))
molf.ploty_IFD_PER
